### 2017-09-30 Graduate - Introduction to Analysis I/Assignment 4/4-homework20170925.tex
update

>>>>

\bigskip
\textbf{Collaborators:} None
\smallskip

\textbf{Solution:}
For $\epsilon > 0$, according to Lusin's Theorem, there exists a closed subset $F$ of $I$, s.t. $m(I\setminus F) < \epsilon$, and $f$ is continuous on $F$.
% Assume $\bigcup_{i=1}^\infty O_i$ is an open cover of $F$, in which $O_{i}$ are open intevals. Then since $F$ is closed there exists a finite open cover, denoted by $\bigcup_{i=1}^n O_i.$ Then
% $$
% F = \bigcup_{i=1}^n (O_i\cap F).
% $$
% Denote $F_{i} = O_{i}\cap F$, then 
% Since $f$ is continuous on $F$, 
Then for $x_0\in F$, for this $\epsilon > 0$, 
$$
\exists \sigma > 0, ~\forall x\in (x_0-\delta, ~x_0+\delta)\cap F, ~|f(x)-f(x_0)| < \epsilon.
$$
Since
$$
\bigcup_{x_0\in F} (x_0-\delta_i, ~x_0+\delta_i)
$$
is an open cover of the closed set $F$, it has a finite subcover, denoted by
$$
\bigcup_{i=1}^n (x_i-\delta_i, ~x_i+\delta_i).
$$
If we define
$$
h = \left\{
\begin{aligned}
&f(x_i), ~\text{for} ~x\in (x_i-\delta_i, ~x_i+\delta_i), \\
&0, ~\text{others}
\end{aligned}
\right.
$$
then $h$ takes constant values in finite intervals, and $h = 0$ in other parts, we know $h$ is a step function. And from the construction above, on each interval $(x_i-\delta_i, x_i+\delta_i)\cap F$, 
$$
|h-f|< \epsilon ~\text{on}~ (x_i-\delta_i, x_i+\delta_i)\cap F.
$$
Thus $h$ is the step function needed.

\bigskip
